Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}

### 2022-11-17 nakayama/paper.tex
Added comment about inclincluding more code from the formal proof

>>>>

\emily[inline]{Emily:  Reflecting, I think it would be very valuable to include the formal proof.  Pieces would work, though it is short, and it could be ``broken up'' among the description of the informal argument.  As is, our description of the proof focuses on the informal argument, which is not new/interesting. }
